---
title: "Untitled"
author: "Xiangxiong Feng"
date: "2023-10-14"
output: github_document
---


```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
library(patchwork)
library(dplyr)

library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```



# Problem 1

```{r}

data("instacart")
instacart = 
  instacart |> 
  as_tibble()
```

```{r}
instacart |> 
  count(aisle) |> 
  arrange(desc(n))
```

```{r}
instacart |> 
  count(aisle) |> 
  filter(n > 10000) |> 
  mutate(aisle = fct_reorder(aisle, n)) |> 
  ggplot(aes(x = aisle, y = n)) + 
  geom_point() + 
  labs(title = "Number of items ordered in each aisle") +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
```
```{r}
instacart |> 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) |>
  group_by(aisle) |> 
  count(product_name) |> 
  mutate(rank = min_rank(desc(n))) |> 
  filter(rank < 4) |> 
  arrange(desc(n)) |>
  knitr::kable()
```


```{r}

instacart |>
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) |>
  group_by(product_name, order_dow) |>
  summarize(mean_hour = mean(order_hour_of_day)) |>
  pivot_wider(
    names_from = order_dow, 
    values_from = mean_hour) |>
  knitr::kable(digits = 2)
```





## Problem 2

```{r}
data("brfss_smart2010")


```

# data cleaning 
```{r}

brfss_smart2010 =
  brfss_smart2010 |>
  janitor::clean_names() |>
  filter(topic == 'Overall Health',
         response %in% c('Excellent', "Very good", "Good", "Fair", "Poor")) |>
  mutate(response = factor(response, 
                           levels = c("Poor", "Fair", "Good",
                                                "Very good","Excellent"), 
                           ordered = TRUE))|>
  rename(state = locationabbr, location = locationdesc)

```

# Question 1
```{r}
#count which states were observed at 7 or more locations in 2002
brfss_smart2010_2002 = 
  brfss_smart2010 |>
  filter(year==2002)|>
  group_by(state, location)|>
  summarize(n_obs = n())|>
  count(state)|>
  filter(n>=7) 
Morethanseven_2002 = as.list(brfss_smart2010_2002$state)

#count which states were observed at 7 or more locations in 2002
brfss_smart2010_2010 = 
  brfss_smart2010 |>
  filter(year==2010)|>
  group_by(state, location)|>
  summarize(n_obs = n())|>
  count(state)|>
  filter(n>=7) 
Morethanseven_2010 = as.list(brfss_smart2010_2010$state)

```

In 2002, `r Morethanseven_2002` were observed at 7 or more locations. In 2010, `r Morethanseven_2010` were observed at 7 or more locations.


# Question 2

```{r}
Excellent_brfss = 
  brfss_smart2010|>
  filter(response == 'Excellent')|>
  select(year, state, data_value)|>
  group_by(year, state) |>
  summarize(
    mean_data_value = mean(data_value)
  )


Excellent_brfss |>
  ggplot(aes(x=year, y = mean_data_value)) +
  geom_line(aes(color = state), alpha = .5)
  
```



# Quesiton 3

```{r}
plot_data_2006 = 
  brfss_smart2010 |>
  filter(year == 2006, state == 'NY') 
  
plot_2006 = 
  plot_data_2006|>
  ggplot(aes(x=response, y = data_value)) +
  ggtitle('distribution of data_value in 2006')+
  geom_violin(aes(fill = response))+
  theme(legend.position = 'none')
  

plot_data_2010 = 
  brfss_smart2010 |>
  filter(year == 2010, state == 'NY') 
  
plot_2010 = 
  plot_data_2010|>
  ggplot(aes(x=response, y = data_value)) +
  ggtitle('distribution of data_value in 2006')+
  geom_violin(aes(fill = response))


plot_2006+plot_2010
```


## Problem 3

```{r}
accel_df =
  read_csv('data/nhanes_accel.csv')|>
  janitor::clean_names()|>
  drop_na()

tidy_accel_df = 
  pivot_longer(
    accel_df,
    min1:min1440,
    names_to = 'MIN',
    values_to = 'MIMS'
  )
```

```{r}
demog_df =
  read_csv('data/nhanes_covar.csv')|>
  janitor::clean_names()|>
  drop_na()|>
  filter(age>= 21)|>
  mutate(education = factor(education, 
                           levels = c("1", "2", "3"), 
                           ordered = TRUE))



```

```{r}
results_data_tidy = 
  full_join(demog_df, tidy_accel_df, by='seqn')|>
  drop_na()|>
   mutate(
     sex = 
      case_match(
        sex, 
        1 ~ "male", 
        2 ~ "female"))

results_data_untidy = 
  full_join(demog_df, accel_df, by='seqn')|>
  drop_na()|>
   mutate(
     sex = 
      case_match(
        sex, 
        1 ~ "male", 
        2 ~ "female"))
  
```



# Table fir number of men and women in each education category
```{r}
results_data_untidy |>
  select(sex, education)|>
  group_by(education)|>
  count(education, sex)|>
  knitr::kable()
 

```

The table is showing the number of men and women in each education category. We can see that numbers of men and women are  close in 1 and 3 education level but a relatively large diffierence in education 2 level.


# visualization of the age distributions for men and women in each education category. Comment on these items 


```{r}
results_data_untidy |>
  ggplot(aes(x=education, y = age)) +
  geom_boxplot(aes(color = sex))
```

This is a boxplot showing the age distributions for men and women in each education category. From the plot, we can see that the biggest difference occurs in education level 2. 


# Plot  total activities (y-axis) against age (x-axis)
```{r}
total_act_df =
  results_data_untidy




  
  
  
```



